%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
\usepackage{fontawesome5}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge Alexey Sokolovskiy} \\ \vspace{1pt}
    \small \href{https://t.me/asokol123}{\underline{\faIcon{telegram} asokol123}} $|$ \href{mailto:alexej.sokolovskiy@gmail.com}{\underline{alexej.sokolovskiy@gmail.com}} $|$ 
    % \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/jake}} $|$
    \href{https://github.com/asokol123}{\underline{\faIcon{github} github.com/asokol123}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Higher School of Economics}{Moscow, Russia}
      {BA, Computer Science}{Aug. 2018 -- Jun 2022}
    \resumeSubheading
      {Yandex Data School (center of additional education for programmers)}{Moscow, Russia}
      {Big data infrastructure}{Sep. 2020 -- Jun 2022}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
    \resumeSubheading
      {Rust Software Engineer}{Feb. 2022 -- Mar. 2023}
      {High NU HFT}{Remote}
      \vspace{0pt}\\
      \hspace{10pt}
      Infrastructure team (Rust)
      \vspace{-7pt}
      \resumeItemListStart
        \resumeItem{Created service to store $>$ 20TB of market events and use it in simulation.}
        \resumeItem{Developed service to gather, compress, store and monitor $>$ 10TB of logs.}
        \resumeItem{Speeded up simulation and ML models training by creating distributed computation service.}
        \resumeItem{Improved parsing speed by 3 times by profiling, improving data deserialization and using reference structures.}
        \resumeItem{Developed and supported pixel ~-- main service for researches to view and analyze market data.}
        \resumeItem{Improved latency q50-95 by 2 times introducing specialized http client.}
        \resumeItem{Improved simulator reliability by creating cgroups and limiting memory and cpu usage.}
        \resumeItem{Decreased latency by 50\% by using AWS API to find best VM configuration.}
      \resumeItemListEnd

    \resumeSubheading
      {Software engineer intern}{Jun. 2021 -- Nov 2021}
      {Yandex LLC}{Moscow, Russia}
      \vspace{0pt}\\
      \hspace{10pt}
      User sessions team (C++, Big data)
      \vspace{-7pt}
      \resumeItemListStart
        \resumeItem{Saved 200 PB of space by migrating data to new format.}
        \resumeItem{Improved data processing speed by 10\% by rewriting legacy algorithm.}
        \resumeItem{Made changing data format much easier by creating data consistency tests.}
      \resumeItemListEnd

    \resumeSubheading
      {Software engineer/Research intern}{Jun. 2020 -- Nov. 2020}
      {Ozon technologies}{Moscow, Russia}
      \vspace{0pt}\\
      \hspace{10pt}
      Price monitoring team (Golang, Python, SQL, HTML/CSS)
      \vspace{-7pt}
      \resumeItemListStart
        \resumeItem{Found several ways of bypassing variti, incapsula, qrator and selectel anti-bot protection.}
        \resumeItem{Implemented web crawler for downloading and parsing $>$1M products per day.}
        \resumeItem{Created a few utilities for detecting crawlers.}
    \resumeItemListEnd


    \resumeSubheading
      {Software engineer intern}{Jun. 2019 -- Nov 2019}
      {Yandex LLC}{Moscow, Russia}
      \vspace{0pt}\\
      \hspace{10pt}
      User sessions team (C++, Python, Big data)
      \vspace{-7pt}
      \resumeItemListStart
        \resumeItem{Created a new monitoring system allowing other teams to detect errors 10 times faster.}
        \resumeItem{Developed a new service of real-time session building leading to 30 times faster metrics calculation.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/asokol123/SecretsStorage}{\color{blue}{Secret Storage}}} $|$ \emph{Python, FastAPI, Docker Compose, MongoDB, Git, TravisCI}}{}
          \resumeItemListStart
            \resumeItem{Developed a REST API application with uvicorn serving a REST API.}
            \resumeItem{Implemented secrets expiration and storing encrypted secrets instead of plain text.}
            \resumeItem{Used MongoDB for asynchronous database operations.}
            \resumeItem{Configured TravisCI for testing and building automation.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section {CTF}
\begin{itemize}[leftmargin=0.15in]
  \setlength\itemsep{-5px}
  \item Member of \href{https://ctftime.org/team/83435}{\color{blue}{C4T BuT S4D}} team since 2019.
  \item Top-4 worldwide team according to \href{https://ctftime.org}{\color{blue}{ctftime}} rating among more than 5000 teams.
  \item Winner of justCTF, FAUST CTF, ENOWARS, p4ctf, and many more
  \item 16-th place at Google CTF 2022, 24-th place at DEF CON 2022 qualifier
  \item Tested \href{https://github.com/C4T-BuT-S4D/ctfcup-2022-stage3-part1}{\color{blue}{solidity stage}} of Russia CTF Cup 2022, solved most challenges at \href{https://capturetheether.com/challenges/}{\color{blue}{Capture the Ether}}.
\end{itemize}

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Rust, C++, Python, Solidity, Golang} \\
     \textbf{Tools}{: Git, Docker, GitHub Actions} \\
     \textbf{Other skills}{: Linux, MongoDB, Grafana, Apache Kafka, Kubernetes, Map-Reduce experience}
    }}
 \end{itemize}

\section{Awards}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{2022}{: Google Code Jam 3rd round participant} \\
    \textbf{2019}{: Google Code Jam 2nd round participant} \\
    \textbf{2018}{: 1st degree award in the national stage of the Russian National Olympiad in Programming, 26th of over 50000 participants} \\
    \textbf{2017}{: 3st degree award in the national stage of the Russian National Olympiad in Programming, 116th of over 50000 participants} \\
    \textbf{2016-2018}{: Various awards at numerous other competitions} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}

